<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-11-30 MainAnalysis.Rmd
Added output of log-likelihood gradient at starting values. Tweaked get_starts.R again

### do 1-Compartment fit
system.time(
  capture.output(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt.data,
      model = "1compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
    ),
    file = paste0("inst/ext/PK_fit_table_1comp_output_",
                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                  ".txt")
  )
)

@@

### do 2-Compartment fit
system.time(
  capture.output(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt.data,
      model = "2compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
    ),
    file = paste0("inst/ext/PK_fit_table_2comp_output_",
                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                  ".txt")
  )
)

>>>>

### do 1-Compartment fit
system.time(
  capture.output(
    PK.fit.table.1comp <- fit_all(
      data.set = cvt.data,
      model = "1compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
  ),
  file = paste0("inst/ext/PK_fit_table_1comp_output_",
                format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                ".txt"),
  type = "message"
  )
)

@@

### do 2-Compartment fit
system.time(
  capture.output(
    PK.fit.table.2comp <- fit_all(
      data.set = cvt.data,
      model = "2compartment",
      modelfun = "analytic",
      compound.col = "analyte_name_original",
      dtxsid.col = "dsstox_substance_id",
      cas.col = "dsstox_casrn",
      reference.col = "fk_reference_document_id",
      species.col = "species",
      species.weight.col = "weight_kg",
      species.weight.units.default = "kg",
      dose.col = "dose_level_normalized",
      time.col = "time_hr",
      time.units.default = "hr",
      media.col = "conc_medium_normalized",
      media.units.default = "normalized",
      value.col = "conc",
      units.default = NA,
      route.col = "administration_route_normalized",
      source.col = "document_id",
      loq.col ="calc_loq",
      subject.default = NA,
      info.default = NA,
      suppress.messages = FALSE
    ),
    file = paste0("inst/ext/PK_fit_table_2comp_output_",
                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
                  ".txt"),
    type = "message"
  )
)
